Implementation Design Patters for Pursuit-Evasion Problems with Bounded Speed

### 2012-11-30 paper.tex
compiled PDF images
further work; genereal commit

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{algorithm2e}

@@

@@

@@

% mathematical definitions and/or data structures
To start, we will begin by defining the scenario environment as an open set \(R\subset\mathbb{R}^2\). \(R\) is to be a simply-connected and has some sort of polygonal boundary. Some scenarios define that \(R\) has holes. \(P\subset R\) is assumed to be the set of points that represent the locations of the various pursuers of the scenario. Accordingly \(E\subset R\) is assumed to make up the set of evaders, their locations being represented as points as well. Members of \(P\) has perfect information about their location with respect to \(R\) and each other, but not necessarily \(E\). Both pursuers and evaders move at various speeds within \(R\). Members of \(P\) generally are expected to move at a bounded consistent speed \(V_P\), while evaders can be viewed as having either a bounded speed or in some cases, unbounded. \cite{limVis, robotics} Pursuers are generally considered to have "caught" the evaders when being within a certain distance of them.

@@

\section{Blended Paradigm Concept}
% explanation of the paradigm (NP-hardness aleviation)
% mathematical definitions and/or data structures
% general setup and rules of "play"
% delunay triangulation and minimum spanning tree connection
% visibility and contamination representation
% tesslation through barycenters
% strategic issues

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{algorithm2e}
\usepackage{graphicx}
\usepackage[font={small,it}]{caption}

\graphicspath{{./gfx/}}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.4\textwidth]{"graph1"}
\caption{An example of a Discrete Formulation on a closed graph; evaders and pursuers are marked accordingly as \(P_1,P_2,E_1,E_2,E_3\)}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.7\textwidth]{"graph2_steps"}
\caption{An example scenario on a graph with three steps where the pursuer wins. Note that in this example the evader \(E_1\) must move each turn. If \(E_1\) is able to "stay put" on a turn it can evade \(P_1\) indefinitely}
\end{figure}

@@

To start, we will begin by defining the scenario environment as an open set \(R\subset\mathbb{R}^2\). \(R\) is to be a simply-connected and has some sort of polygonal boundary. Some scenarios define that \(R\) has holes. \(P\subset R\) is assumed to be the set of points that represent the locations of the various pursuers of the scenario. Accordingly \(E\subset R\) is assumed to make up the set of evaders, their locations being represented as points as well. Members of \(P\) has perfect information about their location with respect to \(R\) and each other, but not necessarily \(E\). Both pursuers and evaders move at various speeds within \(R\). Members of \(P\) generally are expected to move at a bounded consistent speed \(V_P\), while evaders can be viewed as having either a bounded speed or in some cases, unbounded. \cite{limVis, robotics} Pursuers are generally considered to have "caught" the evaders when being within a certain distance of them.

@@

\section{Blended Paradigm Concept}
% explanation of the paradigm (NP-hardness aleviation)
The aim of this section is to present a paradigm that attempts to combine both advantages of the Discrete and Continuous Formulations for pursuers in a real-time environment. We'll refer to this as the \emph{Blended Paradigm} from now on. The Blended Paradigm works on the idea of having a Discrete Formulation model stored, and update it's state according to observed stimuli found in the Continuous Formulation. Subsequently we make strategic decisions for pursuers in the Discrete Model, and execute them in the Continuous Formulation. This allows us to take advantage of the Discrete Formulation's simplified structure and the Continuous Formulation's real-life applications.

% mathematical definitions and/or data structures
To start, we will begin by defining the scenario environment as an open set \(R\subset\mathbb{R}^2\). \(R\) is to be a simply-connected and has some sort of polygonal boundary. Let sets \(P,E\subset{R}\) be the positions of the pursuers and evaders and their velocities identical to that found in the Continuous Formulation. Let \(G\) be an undirected, weighted-edge graph representing \(R\), with each of its vertex in a state being either \emph{visible, uncontaminated,} or \emph{contaminated}. Later in this section we will explain how \(G\) represents \(R\). Each pursuer and evader will keep track of which vertex it currently "occupies". It is also assumed that all pursuers in \(P\) know their location relative to \(R\).

% delunay triangulation and minimum spanning tree connection
To have \(G\) represent \(R\), we take advantage of \(R\)'s shape being a closed polygon. By performing, a Delaunay Triangulation on \(R\), we acquire a triangulation composed of \(R\)'s vertices. \cite{dTri} It is assumed that the triangles outside of \(R\) are "stripped" and discarded immediately. We are left with a set of adjacent triangles that make up \(R\). For each triangle, add a corresponding vertex to \(G\) and add an edge between each adjacent triangle. The weight of an edge between two triangle's vertices is the distance between each triangle's midpoint in barycentric coordinates. \cite{bCenter} \(G\) now represents a set of general areas in \(R\) and the approximate distances between each.

%sexy diagram

A running scenario for the Blended Paradigm looks incredibly similar to the Continuous Formulation. The main difference is that instead of managing sets of changing visibility polygons, visibility is generalized into triangular sections which are managed in \(G\). Let is be assumed for a pursuer to "catch" an evader, they must both be inside the same triangulated region. In real-time, a pursuer checks at each moment which triangulated regions it can completely see. If a region can be completely seen in \(R\) it is marked as visible in \(G\). A triangulated region that was once visible in \(R\) but subsequently no longer is considered uncontaminated. Regions that have never been visible are considered contaminated.

Contaminated triangles and vertices in \(G\) are meant to represent regions in \(R\) where an evader could possibly be. In that case, if a contaminated region is adjacent to an uncontaminated region, it is possible that an evader could move from the contaminated to the uncontaminated region, making both uncontaminated. This creates a degree of "spreading" contamination that needs to be kept in check by the pursuers. Since the evaders move at a bounded speed though, it can be expected that contamination does not happen necessarily instantaneously. For this reason the edges in \(G\) have a weight associated with them. Contamination from one vertex/triangle to another happens at a speed: \begin{displaymath}
foo penis
\end{displaymath}

% tesslation through barycenters
% strategic issues

@@

\bibitem{dTri}
  \emph{Delaunay Triangulation},
  Wolfram Mathworld,
  Retrieved November 2012

\bibitem{bCenter}
  \emph{Barycentric Coordinates},
  Wolfram Mathworld,
  Retrieved November 2012
